### 2022-09-23 Thesis/text/diskussion.tex
almost done, summary not finished, introduction is not polished

\section{Conclusion}

\section{Prospect}

>>>>

What went well? 
This thesis demonstrated a way on how to incorporate advanced behavior planning in ROS2 mobile robots. The goal was to achieve higher levels of autonomy and robustness. The implemented behaviors and the system supervision component have shown to improve the behavior in the simulated scenarios.

However, the results will need to be reproduced on a real mobile robot. Additionaly, the implemented behaviors are a first step to increase the autonomy, but many more behaviors and fallbacks need to be created for the behavior planner.

The used system architecture is a good base upon which more development can take place without running into problems or limitations in later stages of the development.

More work is needed to define what is considered to be a safe state or position for the robot to be in after an emergency stop is triggered. Reaching these minimum risk states after emergencies is then the duty of the behavior planner.

Some behaviors that incorporate rules for autonomous driving, like keeping appropriate distances, right of way, etc., into the planning need to be implemented in future works.

Right now, the robot has no special behaviors for multi-robot system which is a field for many more deliberative behaviors like sharing sensor data with other robots to overcome complete sensor failures.

What is missing? Further development?

New research questions?

### 2022-09-23 Thesis/text/implementierung.tex
almost done, summary not finished, introduction is not polished

\section{System Architecture}
\begin{figure}
	\includegraphics[width=1.0\textwidth]{images/component_diagram_bt_architecture.png}
	\caption{Component Diagram of System Architecture}
\end{figure}

@@

@@

@@

The original goal is then republished to replan the global path on the updated map.

@@

\begin{figure}
	\includegraphics[width=0.75\textwidth]{images/global_planning_fallback.png}
	\caption{Path Planning Fallback}
\end{figure}

>>>>

\section{System Architecture}

The system architecture, depicted in figure xx, integrates the behavior tree, responsible for the behavior planning, in a position to override Navigation2. This is done through the help of the Decision Gate, that can selectively forward speed commands to the robot controller. 
The behavior tree can access the sensor data when needed through the Data Backup component. The System Supervision component controls the health of all components, but the connections are not depicted in the component diagram for Übersichtlichkeit.

\begin{figure}[h!]
	\includegraphics[width=1.05\textwidth]{images/component_diagram_bt.png}
	\caption{Component Diagram of System Architecture}
\end{figure}

@@

This component is responsible for modyfying or blocking the Velocity Commands from Nav2. The component receives messages from Navigation2 on the "/cmd$\_$vel$\_$nav" topic and on the "/cmd$\_$vel$\_$bt" topic from the behavior tree. This component publishes the received messages on the actual topic "/cmd$\_$vel" which is subscribed by the robot controller. 
The BT can modify parameters of the Decision Gate, to either disregard incoming messages of Nav2 completely or to modify them. The modification is useful when the situation demands the robot to slow down. If the Decision Gate receives messages from both Nav2 and the BT, it will prioritize the BT. This situation should theoretically never occur as the BT will set the parameters for the Decision Gate accordingly and/or cancel the current Navigation Goal before publishing commands on its own. It is implemented as an additional safety measure, in case the cancellation of the goal is not possible if Navigation2 is not responsive to the cancellation command.

@@

\begin{figure}[h!]
	\includegraphics[width=1.0\textwidth]{images/simplified_bt.png}
	\caption{Top Level Behavior Tree Structure}
\end{figure}

@@

The original goal is then republished to replan the global path on the updated map. A more detailed view of the whole behavior is depicted in figure xx.

\begin{figure}
	\includegraphics[width=0.9\textwidth]{images/activity_diagram_collision.png}
	\caption{Activity Diagram for the Collision Behavior}
\end{figure}

@@

\begin{figure}[h!]
	\includegraphics[width=0.7\textwidth]{images/global_planning_fallback.png}
	\caption{Path Planning Fallback Behavior}
\end{figure}

\section{System Support Tools}
\subsection{Gazebo Sensor Drivers}
For testing purposes, the simulated sensor data is not published directly on to the actual topic by gazebo. To control the flow of information in the system, an intermediary node is used, which subscribes to the Gazebo topic and republishes the information on the original topic. With this methodology, the failure of a sensor can be simulated as the simulation does not offer this functionality. Figure xx shows the RQT graph, which depicts the ROS nodes and their subscribed/published topics.

\begin{figure}
	\includegraphics[width=0.75\textwidth]{images/rqt_graph_sensor_drivers.png}
	\caption{Graph for the Sensor Driver nodes and topics}
\end{figure}

\subsection{Custom ROS Interfaces}

Because of the neccessity to have ROS nodes spinning outside of the BT thread as discussed in 4.4.1, additional interfaces needed to be created in order to receive informations through service calls. The created service types are listed in table xx. All of the service definitions are created in a dedicated package named "bt$\_$msgs".

\begin{table}[h!]
	\caption{Implemented Custom Services}
	\begin{tabular}{ | m{0.2\textwidth} | m{0.33\textwidth}| m{0.33\textwidth} | m{0.2\textwidth} |} 
  	\hline
  	Name & Request & Response \\ 
  	\hline
  	GetCharge & Empty & float charge, float idle$\_$decrease$\_$per$\_$sec, float drive$\_$decrease$\_$per$\_$sec \\
  	\hline
  	GetDistance & Empty & float distance$\_$in$\_$meter\\ 
  	\hline
  	GetLastGoal & Empty & geometry$\_$msgs/Pose last$\_$goal$\_$pose \\ 
  	\hline
  	GetLastMap & Empty & nav$\_$msgs/OccupancyGrid map \\
  	\hline
  	GetTwistArray & Empty & geometry$\_$msgs/Twist[] cmd$\_$vel$\_$array\\
  	\hline  	
  	PubCmdVel & geometry$\_$msgs/Twist cmd$\_$vel, float time$\_$in$\_$seconds & bool success \\
  	\hline
  	SendUpdatedMap & nav$\_$msgs/OccupancyGrid updated$\_$map & Empty \\
  	\hline
	\end{tabular}
\end{table}
